Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-10-25 manuscript/manuscript.Rmd
Expanding upon the use of IS and including links to github

This shift in metabolite abundance was largely driven by a corresponding shift in biomass. Particulate carbon and summed metabolite concentration were tightly correlated across all samples and depths (Type I linear regression $\beta = 24.9\pm1.82$ (SE), Pearson's $r$ = 0.813, p-value < 0.001, Supplemental Figure 2). This overall trend was largely driven by higher values at 15 meters and the DCM than at depth, but when analyzed at each depth individually the general correspondence held (Supplemental Figure 2). The DCM and 175 meter samples had the stronger trends ($\beta_{DCM} = 22.6\pm5.53$, $r= 0.593$, p-value < 0.001; $\beta_{175m} = 23.9\pm7.36$, $r= 0.503$, p-value = 0.003) while 15 meter samples showed no significant relationship ($\beta_{15m} = 3.4\pm12.9$, $r= 0.049$, p-value = 0.792). This meant that metabolites contributed a relatively fixed fraction of carbon to the particulate pool with our 53 quantified metabolites representing between 1.5% and 5% of the carbon in the system (Figure 3). Particulate nitrogen was tightly correlated with particulate carbon ($r=0.933$) but the fraction of particulate nitrogen represented by the quantified metabolites was slightly higher across the transect with contributions typically between 2% and 6%.

>>>>

This shift in metabolite abundance was largely driven by a corresponding shift in biomass. Particulate carbon and summed metabolite concentration were tightly correlated across all samples and depths ($\beta = 24.9\pm1.82$ (SE), Pearson's $r$ = 0.813, p-value < 0.001, Supplemental Figure 2). This overall trend was largely driven by higher values at 15 meters and the DCM than at depth, but when analyzed at each depth individually the general correspondence held (Supplemental Figure 2). The DCM and 175 meter samples had the stronger trends ($\beta_{DCM} = 22.6\pm5.53$, $r= 0.593$, p-value < 0.001; $\beta_{175m} = 23.9\pm7.36$, $r= 0.503$, p-value = 0.003) while 15 meter samples showed no significant relationship ($\beta_{15m} = 3.4\pm12.9$, $r= 0.049$, p-value = 0.792). This meant that metabolites contributed a relatively fixed fraction of carbon to the particulate pool with our 53 quantified metabolites representing between 1.5% and 5% of the carbon in the system (Figure 3). Particulate nitrogen was tightly correlated with particulate carbon ($r=0.933$) but the fraction of particulate nitrogen represented by the quantified metabolites was slightly higher across the transect with contributions typically between 2% and 6%.
